\documentclass[letterpaper,11pt]{article}

\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}
\usepackage[margin=1.4cm]{geometry}

\pdfgentounicode=1

% Styling
\pagestyle{empty}

\addtolength{\oddsidemargin}{-0.38cm}
\addtolength{\textwidth}{0.76cm}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}\vspace{0pt}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

%----------HEADING----------
\begin{center}
  {\Large \scshape Augustas Vaivada}\\[2mm]
  {\footnotesize
    \raisebox{-0.1\height}{\faPhone}\ \underline{\href{tel:+37067417628}{+370 674 17628}}\ ~
    \raisebox{-0.1\height}{\faEnvelope}\ \underline{\href{mailto:augustasv16@gmail.com}{augustasv16@gmail.com}}\ ~
    \raisebox{-0.1\height}{\faLinkedin}\ \underline{\href{https://www.linkedin.com/in/augustas-vaivada}{linkedin.com/in/augustas-vaivada}}\ ~
    \raisebox{-0.1\height}{\faGithub}\ \underline{\href{https://github.com/aujezus}{github.com/aujezus}}\ ~
    \raisebox{-0.1\height}{\faGlobe}\ \underline{\href{https://aujezus.com}{aujezus.com}}
  }
  \vspace{-8pt}
\end{center}

%----------- EDUCATION -----------
\section*{Education}
\vspace{1mm}

\resumeSubHeadingListStart
  \resumeSubheading
    {Vilnius University}{Expected Graduation: Jan 2028}
    {\href{https://www.vu.lt/studijos/stojantiesiems/bakalauro-studiju-sarasas/informacines-technologijos}{Bachelor in Information Technology}}{}
            \\[5mm]
    

\resumeItemListStart
  \resumeItem{Coursework: Discrete Mathematics, Data Structures, OOP, UNIX, DBMS, Computer Networks, Virtualization, Software Engineering, HCI, Internet Technologies, Security, Systems Architecture.}
  \resumeItem{Program: Project-based with industry collaboration, modern, cloud-ready infrastructure.}
  \resumeItem{Recognition: \textbf{“Investors’ Spotlight” award} (2017) for best alignment with investor needs among Lithuanian university programs.}
\resumeItemListEnd

 \vspace{-15pt}

 \resumeProjectHeading
            {\textbf{NKKM Computer School}} {Graduated: 2022}
            \\[5mm]
          \resumeItemListStart
            \resumeItem{Application programming with \textbf{Visual Basic, Python, and C\#}.}
            \resumeItem{Unity game development, cloud technologies, remote management and security.}
            \resumeItem{Website development with \textbf{JS, HTML, CSS}.}
          \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-12pt}

%-----------Experience---------------
\section{Work Experience}
    \resumeSubHeadingListStart
                \resumeSubheading{UAB Ababa}{Oct 2024 -- Oct 2025}{Junior Full Stack Engineer}{Remote} 
                \resumeItemListStart
                      \resumeItem{Delivered \textbf{500+ full‑stack features} (public pages, external API integrations, CRM workflows) using \textbf{NestJS}, \textbf{React}, and \textbf{PostgreSQL}, reducing backlog tickets by \textbf{35\%}.}
                    \resumeItem{Optimized and upgraded a \textbf{canvas‑style editor in React}, cutting render latency by \textbf{40\%} and achieving \textbf{pixel‑perfect} PDF exports.}
                    \resumeItem{Integrated \textbf{12+} external APIs - including Stripe (subscriptions), Neopay, Brevo, Mailtrap, Elpako, and Discord - leveraging \textbf{RESTful} architecture and event‑driven \textbf{webhooks}.}
                    \resumeItemListEnd
            \resumeSubheading{UAB Ababa}{Aug 2024 -- Oct 2024}{Full Stack Engineer Intern}{Remote} 
                \resumeItemListStart
                     \resumeItem{Resolved \textbf{40+} UI/backend bugs across \textbf{React} and \textbf{NestJS} services, improving stability.}
                    \resumeItem{Implemented \textbf{30}+ entry‑level features (CRUD endpoints, simple CRM logic, form validations) using \textbf{NestJS, React, and PostgreSQL}, adhering to code review standards and style guides.}
                    \resumeItem{Refactored legacy components and \textbf{NestJS} modules by removing dead code and extracting reusable \textbf{React hooks}, cutting bundle size by \textbf{10\%} and simplifying future feature work.}
                    \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-12pt}

%-----------PROJECTS-----------
\section{Projects} 
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
            {\textbf{Žaidimų Pieva} \,|\, \emph{\href{https://zaidimu-pieva.vercel.app/}{Website}} \,|\, \emph{\href{https://github.com/AuJezus/zaidimu-pieva}{Source Code}}}{NextJS \,|\, Tailwind \,|\, Contentful}
            \\[5mm]
          \resumeItemListStart
            \resumeItem{Built and deployed a marketing site for a lawn‑game rental business using Next.js, TypeScript, Tailwind, and shadcn/ui, featuring a responsive “wave” design.}
            \resumeItem{Implemented headless CMS with \textbf{Contentful} and a serverless contact flow via \textbf{Web3Forms}, enabling non‑technical content updates and generating qualified leads to email.}
          \resumeItemListEnd
 \vspace{-20pt}
 \resumeProjectHeading
            {\textbf{Portfolio/Blog} \,|\, \emph{\href{https://www.aujezus.com/}{Website}} \,|\, \emph{\href{https://github.com/AuJezus/personal-website-v3}{Source Code}}}{NextJS \,|\, Tailwind \,|\, PostgreSQL}
            \\[5mm]
          \resumeItemListStart
            \resumeItem{Built my portfolio with Next.js, TypeScript, Tailwind, shadcn/ui, \textbf{Velite} and \textbf{React Email} - featuring a custom animated hero, blog with \textbf{MDX + TOC}, and \textbf{parallel/intercepting route} modals for project previews.}
            \resumeItem{Implemented forms using \textbf{React Hook Form + Zod} with \textbf{server actions}, and set up email workflows via \textbf{React Email + Nodemailer}. Added live “stats” in navigation via \textbf{Wakatime and Last.fm APIs}.}
          \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}

  %-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{   
     \textbf{Languages}{: JavaScript/TypeScript, CSS, HTML5, C\#, SQL, Python} \\[1mm]
     \textbf{Developer Tools}{: Vercel, Postman, Git, Docker, Jira, AWS, Supabase.} \\[1mm]
     \textbf{Libraries/Frameworks}{: ReactJS, Redux, Tailwind, NodeJS, NextJS, ExpressJS, NestJS, Unity.} \\ [1mm]
    }}
 \end{itemize}

\vspace{-18pt}

\end{document}